---
title: "Cancer de mama"
author: "Jose Felix Rojas Cabeza"
subtitle: "Por definir"
date: "`r format(Sys.time(), '%Y / %B / %d')`"
output: 
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    code_folding: show
    theme: cerulean
    toc: yes
    toc_float: yes
params:
  data1: "./Data/BreastCancer1.csv"
  data2: "./Data/WBC.csv"
  ptrain: !r 2/3
  seed_train: 378528 #805547
  seed_alg: 303381   #713945
---
```{r setup, include=FALSE}
require(knitr)
# include this code chunk as-is to set options
opts_chunk$set(comment = NA, prompt = TRUE, tidy = FALSE, 
               fig.width = 7, fig.height = 7,echo = TRUE,
               fig.align='center', message = FALSE, 
               warning = FALSE, cache=TRUE)
Sys.setlocale("LC_TIME", "C")

# Random numbers for seeds: 713945, 805547
```

# Data

## Data collection
```{r}
bc_full <- read.csv(params$data1, stringsAsFactors = FALSE)
# dim(bc_full)
# head(bc_full[1:4])

bc_10 <- read.csv(params$data2, stringsAsFactors = FALSE)
# dim(bc_10)
# head(bc_10[1:4])

names(bc_10)[1]<-paste("ID") # Numero de codigo de muestra #ID
names(bc_10)[2]<-paste("Clump_thickness") # Espesor del grupo 1 - 10
names(bc_10)[3]<-paste("Uniformty_c_size") # Uniformidad del tamano de la célula  1 - 10
names(bc_10)[4]<-paste("Uniformty_c_shape") # Uniformidad de la forma de la célula 1 - 10 
names(bc_10)[5]<-paste("Marginal_adhesion") # Adherencia marginal 1 - 10 
names(bc_10)[6]<-paste("Sing_epith_c_size") # Tamano de la célula epitelial unica  1 - 10
names(bc_10)[7]<-paste("Bare_nuclei") # Nucleos desnudos 1 - 10
names(bc_10)[8]<-paste("bland_Chromatina") # Cromatina blanda 1 - 10 
names(bc_10)[9]<-paste("Normal_nucleoli") # Nucleos normales 1 - 10 
names(bc_10)[10]<-paste("Mitosis") # Mitosis 1 - 10 
names(bc_10)[11]<-paste("Class") # Class (2 for Benign, 4 for malignant)

```

```{r}
dim(bc_full)
dim(bc_10)

head(bc_full)
head(bc_10)
```


## Data exploration and preparation

```{r}
# 1234567890123456789012345678901234567890123456789012345678901234567890
bc <- bc_full[,-1]  

bc_s <- bc_10[,-1] 

# Figura 1. Izq
#str(bc)

table(is.na(bc_s))
``` 

```{r}
for (i in 1:length(bc_s$Class)){
  if (bc_s$Class[i]==2) {
  bc_s$Class[i]<-"B"}
  else { bc_s$Class[i]<- "M"
  }}

table(is.na(bc_s))
# EMPIEZAN A SALIR NA's

```

```{r}
bc_s[,1] <- as.numeric(bc_s[,1])
bc_s[,2] <- as.numeric(bc_s[,2])
bc_s[,3] <- as.numeric(bc_s[,3])
bc_s[,4] <- as.numeric(bc_s[,4])
bc_s[,5] <- as.numeric(bc_s[,5])
bc_s[,6] <- as.numeric(bc_s[,6])
bc_s[,7] <- as.numeric(bc_s[,7])
bc_s[,8] <- as.numeric(bc_s[,8])
bc_s[,9] <- as.numeric(bc_s[,9])
bc_s[,10] <- as.character(bc_s[,10])

#str(bc_s)
table(is.na(bc_s))

bc_s <- na.omit(bc_s)

table(is.na(bc_s))

# se pierden 160 datos
```

```{r echo=FALSE}
dim <- dim(bc)
num_train <- round((dim[1]*params$ptrain),0)
num_test <- dim[1] - num_train

dim_s <- dim(bc_s)
num_train_s <- round((dim_s[1]*params$ptrain),0)
num_test_s <- dim_s[1] - num_train_s
```

```{r}
# Benign / Malignant
bc$diagnosis <- factor(bc$diagnosis, levels= c("B", "M"), labels=c("Benign", "Malignant"))
table(bc$diagnosis)

bc_s$Class <- factor(bc_s$Class, levels= c("B", "M"), labels=c("Benign", "Malignant"))
table(bc_s$Class)
```

```{r}
table(is.na(bc))
table(is.na(bc_s))

dim(bc_s)

table(is.na(bc_s))
dim(bc_s)
```

```{r}
normalize <- function(x) {
return ((x - min(x)) / (max(x) - min(x)))
}

bc_n <- as.data.frame(lapply(bc[1:(round(dim[2],0)-1)], normalize))

#bc_z <- as.data.frame(scale(bc[1:(round(dim[2],0)-1)]))

bc_s_n <- as.data.frame(lapply(bc_s[1:(round(dim_s[2],0)-1)], normalize))

#str(bc_n)
str(bc_s)
head(bc_s, 10)
```

```{r}
# Figura 1. der
par(mar=c(11,3,1,1))

means_n <- as.numeric((lapply(bc_n, mean)))

boxplot(bc_n[1:30], las=2, col="lightblue")
# , main="Figura 2. Distribucion de las variables del dataset normalizadas"
abline(h=mean(means_n), col="red")
```

```{R fig.width=9, fig.height=9}
par(mar=c(10,3,1,1))

means_n_s <- as.numeric((lapply(bc_s_n, mean)))

boxplot(bc_s_n[,-1], las=2, col="lightblue")
# , main="Figura 2. Distribucion de las variables del dataset normalizadas"
abline(h=mean(means_n_s), col="red")
```

# Correlogram
```{r, fig.height=15, fig.width=15}
library(corrplot)
par(mar=c(11,3,1,1))

C <- cor(round(as.matrix(bc_n[1:30]), 4))

corrplot(C, method = "pie")

C2 <- cor(round(as.matrix(bc_s_n[1:9]),4))

corrplot(C2, method = "pie")
```

# Creation training and test datasets for 10-fold crossvalidation 
```{r}
# 2021-07-19
library(caret)

bc_n_full <- cbind(bc_n, bc$diagnosis)

names(bc_n_full)[31] <- "diagnosis"

dim(bc_n_full)

set.seed(params$seed_train)

inTrain <- createDataPartition( y = 1:nrow(bc_n_full),
                                p = params$ptrain,
                                list = FALSE )

# KNN, SVM, RF
train <- bc_n_full[inTrain, ]
test <- bc_n_full[-inTrain, ]

table(train[,31])
table(test[,31])

#ANN
#Data Partition
set.seed(params$seed_alg)


inTrain_ann <- createDataPartition(y=bc_n_full$diagnosis, p=round(params$ptrain,4), list=FALSE)


# Normalized dataset
ann_data_n <- cbind(bc_n, bc$diagnosis)
names(ann_data_n)[31] <- "diagnosis"

train_ann <- ann_data_n[inTrain_ann, ]
test_ann  <- ann_data_n[-inTrain_ann, ]

#train.set <- dataset[inTrain,]
#test.set  <- dataset[-inTrain,]

( c(nrow(train)/nrow(test), nrow(train_ann)/nrow(test_ann)) )
# should be around 2

# SMALL DATASET
# bc_s_n refers to Breast Cancer Small dataset Normalized

bc_s_n_full <- cbind(bc_s_n, bc_s$Class)

names(bc_s_n_full)[10] <- "diagnosis"


dim(bc_s_n_full)



inTrain_s <- createDataPartition( y = 1:nrow(bc_s_n_full),
                                p = params$ptrain,
                                list = FALSE )

train_s <- bc_s_n_full[inTrain, ]
test_s <- bc_s_n_full[-inTrain, ]



table(train_s[,10])
table(test_s[,10])

#ANN
#Data Partition
inTrain_s_ann <- createDataPartition(y=1:nrow(bc_s_n_full), 
                                     p=params$ptrain, 
                                     list=FALSE)


# Normalized dataset
ann_data_s_n <- bc_s_n_full 

train_s_ann <- ann_data_s_n[inTrain_ann,]
test_s_ann  <- ann_data_s_n[-inTrain_ann,]

#train.set <- dataset[inTrain,]
#test.set  <- dataset[-inTrain,]

( c(nrow(train_s)/nrow(test_s), nrow(train_s_ann)/nrow(test_s_ann)) )

table(train_s$diagnosis)
table(test_s$diagnosis)


```

# KNN
```{r}
set.seed(params$seed_alg)

start_time <- Sys.time()

ctrl <- trainControl(method="repeatedcv",repeats = 10, number = 10, 
                     classProbs = T, savePredictions = T) 
model_knn <- train(diagnosis ~ ., data = train, method = "knn", 
                   trControl = ctrl, preProcess = c("center","scale"),
                   tuneLength = 20)

end_time <- Sys.time()

(knn_time <- end_time - start_time)
```

## Confusion matrix KNN
```{r}
prediction <- predict(model_knn, test) 
ct <- table(prediction, test$diagnosis) 
(cm_knn <- confusionMatrix(ct, positive="Malignant"))
```

# SVM
```{r}
set.seed(params$seed_alg)

start_time <- Sys.time()

model_svm <- train(diagnosis ~ ., train, method='svmLinear',
               trControl= trainControl(method='cv',number=10,repeats = 10,
                                       classProbs = T,
                                       savePredictions = T),
               tuneGrid= NULL, trace = FALSE)

end_time <- Sys.time()

(svm_time <- end_time - start_time)
```

## Confusion matrix SVM
```{r}
prediction <- predict(model_svm, test) 
ct <- table(prediction, test$diagnosis) 
(cm_svm <- confusionMatrix(ct, positive="Malignant"))
```

# RF
```{r}
set.seed(params$seed_alg)

ctrl <- trainControl( method = "repeatedcv",
                      number = 10,
                      repeats = 10,
                      summaryFunction = defaultSummary,
                      verboseIter = FALSE,
                      classProbs = TRUE,
                      savePredictions = TRUE)
# repeats=3 )

## Tunegrid for Random Forest
# mtry define cuantas variables se seleccionan al azar en cada split. Por
# defecto sqrt(n.variables)
grid_rf <- expand.grid(.mtry = c(2,4,8,16))

start_time <- Sys.time()

model_rf <- train (diagnosis ~ .,
                   data = train,
                   method ="rf",
                   trControl=ctrl,
                   #tuneLength = 9,
                   tuneGrid = grid_rf,
                   metric="Accuracy",
                   prePoc = c("center", "scale"),
                   verbose =FALSE,
                   trace = FALSE
                   )

end_time <- Sys.time()

(rf_time <- end_time - start_time)
```

## Confusion matrix RF
```{r}
pred_rf <- predict (model_rf, newdata = test)

(cm_rf <- confusionMatrix(data=pred_rf, test$diagnosis, positive = "Malignant"))
```

# ANN
```{r}
library(nnet)
library(NeuralNetTools)
```

```{r warning=FALSE,message=FALSE, fig.height=15, fig.width=15}
# 10 fold-crossvalidation model

start_time <- Sys.time()

model_ann <- train(diagnosis ~ ., train_ann, method='nnet', 
               trControl= trainControl(method='cv', number=10), 
               tuneGrid= NULL, tuneLength=10 ,trace = FALSE)


end_time <- Sys.time()

(ann_time <- end_time - start_time)

plotnet(model_ann, alpha=0.6)

summary(model_ann)

prediction_ann <- predict(model_ann, test_ann[-31])                    # predict
table(prediction, test_ann$diagnosis)                                  # compare

# predict can also return the probability for each class:
prediction_ann_prob <- predict(model_ann, test_ann[-31], type="prob") 

head(prediction)
```

# Confusion Matrix ANN

```{r}
(cm_ann <- confusionMatrix(predict(model_ann, test_ann[,-31],type="raw"),
                          test_ann[,31], positive = "Malignant"))
#predict(model, test.set[,31],type="raw")
#test.set[,31]
```

# KNN Small Dataset
```{r}
set.seed(params$seed_alg)

start_time <- Sys.time()

ctrl <- trainControl(method="repeatedcv",repeats = 10, number = 10, 
                     classProbs = T, savePredictions = T) 
model_knn_s <- train(diagnosis ~ ., data = train_s, method = "knn", 
                   trControl = ctrl, preProcess = c("center","scale"),
                   tuneLength = 20)

end_time <- Sys.time()

(knn_time_s <- end_time - start_time)
```

## Confusion matrix KNN Small Dataset
```{r}
prediction <- predict(model_knn_s, test_s) 
ct <- table(prediction, test_s$diagnosis) 
(cm_knn_s <- confusionMatrix(ct, positive="Malignant"))
```

# SVM Small Dataset
```{r}
set.seed(params$seed_alg)

start_time <- Sys.time()

model_svm_s <- train(diagnosis ~ ., train_s, method='svmLinear',
               trControl= trainControl(method='cv',number=10,repeats = 10,
                                       classProbs = T,
                                       savePredictions = T),
               tuneGrid= NULL, trace = FALSE)

end_time <- Sys.time()

(svm_time_s <- end_time - start_time)
```

## Confusion matrix SVM Small Dataset
```{r}
prediction <- predict(model_svm_s, test_s) 
ct <- table(prediction, test_s$diagnosis) 
(cm_svm_s <- confusionMatrix(ct, positive="Malignant"))
```

# RF Small Dataset
```{r}
set.seed(params$seed_alg)

ctrl <- trainControl( method = "repeatedcv",
                      number = 10,
                      repeats = 10,
                      summaryFunction = defaultSummary,
                      verboseIter = FALSE,
                      classProbs = TRUE,
                      savePredictions = TRUE)
# repeats=3 )

## Tunegrid for Random Forest
# mtry define cuantas variables se seleccionan al azar en cada split. Por
# defecto sqrt(n.variables)
grid_rf <- expand.grid(.mtry = c(2,4,8,16))

start_time <- Sys.time()

model_rf_s <- train (diagnosis ~ .,
                   data = train_s,
                   method ="rf",
                   trControl=ctrl,
                   #tuneLength = 9,
                   tuneGrid = grid_rf,
                   metric="Accuracy",
                   prePoc = c("center", "scale"),
                   verbose =FALSE,
                   trace = FALSE
                   )

end_time <- Sys.time()

(rf_time_s <- end_time - start_time)
```

## Confusion matrix RF Small Dataset
```{r}
pred_rf_s <- predict (model_rf_s, newdata = test_s)

(cm_rf_s <- confusionMatrix(data=pred_rf_s, test_s$diagnosis, positive = "Malignant"))
```

# ANN Small Dataset
```{r}
library(nnet)
library(NeuralNetTools)
```

```{r warning=FALSE,message=FALSE, fig.height=15, fig.width=15}
# 10 fold-crossvalidation model

start_time <- Sys.time()

model_ann_s <- train(diagnosis ~ ., train_s_ann, method='nnet', 
               trControl= trainControl(method='cv', number=10), 
               tuneGrid= NULL, tuneLength=10 ,trace = FALSE)

end_time <- Sys.time()

(ann_time_s <- end_time - start_time)

plotnet(model_ann_s, alpha=0.6)

summary(model_ann)

prediction_ann_s <- predict(model_ann_s, test_s_ann[-10])                        # predict
table(prediction, test_s_ann$diagnosis)                                  # compare

# predict can also return the probability for each class:
prediction_ann_s_prob <- predict(model_ann_s, test_s_ann[-10], type="prob")  

head(prediction)
```

```{r}
(cm_ann_s <- confusionMatrix(predict(model_ann_s, test_s_ann[,-10],type="raw"),
                          test_s_ann[,10], positive = "Malignant"))#predict(model, test.set[,31],type="raw")
#test.set[,31]
```

# TABLA 1
```{r}
print("KNN")
cm_knn$overall[1]
cm_knn$overall[2]
cm_knn$byClass

print("SVM")
cm_svm$overall[1]
cm_svm$overall[2]
cm_svm$byClass

print("RF")
cm_rf$overall[1]
cm_rf$overall[2]
cm_rf$byClass

print("ANN")
cm_ann$overall[1]
cm_ann$overall[2]
cm_ann$byClass
```

Tabla 1 Small
```{r}
print("KNN")
cm_knn_s$overall[1]
cm_knn_s$overall[2]
cm_knn_s$byClass

print("SVM")
cm_svm_s$overall[1]
cm_svm_s$overall[2]
cm_svm_s$byClass

print("RF")
cm_rf_s$overall[1]
cm_rf_s$overall[2]
cm_rf_s$byClass

print("ANN")
cm_ann_s$overall[1]
cm_ann_s$overall[2]
cm_ann_s$byClass
```

# CURVAS ROC
```{r fig.height=8, fig.width=8}
library(pROC)

# "royalblue","dodgerblue", "deepskyblue", "lightskyblue"

par(mfrow=c(2,2))

plot.roc(model_knn$pred$obs,
         model_knn$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE, 
         col="royalblue", main = "Curva ROC para kNN")

plot.roc(model_svm$pred$obs,
         model_svm$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="dodgerblue", main = "Curva ROC para SVM")

plot.roc(model_rf$pred$obs,
         model_rf$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="deepskyblue", main = "Curva ROC para RF")

plot.roc(test_ann$diagnosis, 
         prediction_ann_prob$Malignant,  
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="lightskyblue", main = "Curva ROC para ANN")
```



```{r}
# https://stackoverflow.com/questions/46891681/calculating-auc-from-nnet-model 
# https://www.r-bloggers.com/2016/11/calculating-auc-the-area-under-a-roc-curve/ 

#plot.roc(test_ann$diagnosis, 
#         prediction_ann_prob$Malignant, 
#         smoothed = TRUE,
#         legacy.axes=TRUE,
#         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
#         auc.polygon=TRUE, 
#         max.auc.polygon=TRUE, grid=TRUE,
#         print.auc=TRUE, show.thres=TRUE,
#         col="blue", main = "Curva ROC para RF")
```

# Small dataset
```{r fig.height=8, fig.width=8}
library(pROC)

# "royalblue","dodgerblue", "deepskyblue", "lightskyblue"

par(mfrow=c(2,2))

plot.roc(model_knn_s$pred$obs,
         model_knn_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE, 
         col="royalblue", main = "Curva ROC para kNN")

plot.roc(model_svm_s$pred$obs,
         model_svm_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="dodgerblue", main = "Curva ROC para SVM")

plot.roc(model_rf_s$pred$obs,
         model_rf_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="deepskyblue", main = "Curva ROC para RF")

plot.roc(test_s_ann$diagnosis, 
         prediction_ann_s_prob$Malignant,  
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="lightskyblue", main = "Curva ROC para ANN")
```


```{r fig.height=16, fig.width=12}
#cm_knn
#cm_svm
#cm_rf
#cm_ann

par(mfrow=c(3,3), pty="m")

# 12345678901234567890123456789012345678901234567890123456789012345678901234567890

color <- c("royalblue","dodgerblue", "deepskyblue", "lightskyblue")

Acc <- c(cm_knn_s$overall[1], cm_svm_s$overall[1], 
         cm_rf_s$overall[1], cm_ann_s$overall[1])
  
Kappa <- c(cm_knn_s$overall[2], cm_svm_s$overall[2], 
           cm_rf_s$overall[2], cm_ann_s$overall[1])

Sensib <- c(cm_knn_s$byClass[1], cm_svm_s$byClass[1], 
            cm_rf_s$byClass[1], cm_ann_s$byClass[1])

Espec <- c(cm_knn_s$byClass[2], cm_svm_s$byClass[2], 
           cm_rf_s$byClass[2], cm_ann_s$byClass[2])

PPV <- c(cm_knn_s$byClass[3], cm_svm_s$byClass[3], 
         cm_rf_s$byClass[3], cm_ann_s$byClass[3])

NPV <- c(cm_knn_s$byClass[4], cm_svm_s$byClass[4], 
         cm_rf_s$byClass[4], cm_ann_s$byClass[4])

F1 <- c(cm_knn_s$byClass[7], cm_svm_s$byClass[7], 
        cm_rf_s$byClass[7], cm_ann_s$byClass[7])
  
AUC <- c(0.991, 0.994, 0.993, 0.997)

times <- c(knn_time_s, svm_time_s, rf_time_s, ann_time_s)

time_p <- barplot(as.vector(times), names.arg=c("kNN", "SVM", "RF", "ANN"), 
                  col = color, ylab=c("Proporcion"), main="Tiempo")
text(x = time_p, y = times, label = round(times,3), pos = 1, cex = 0.8, col = 
       "black")

Acc_p <- barplot(Acc, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="Exactitud (Accuracy)")
text(x = Acc_p, y = Acc-0.05, label = round(Acc,4), pos = 1, cex = 0.8, col = 
       "black")

K_p <- barplot(Kappa, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="Kappa")
text(x = K_p, y = Kappa-0.05, label = round(Kappa,4), pos = 1, cex = 0.8, col = 
       "black")

Sens_p <- barplot(Sensib, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="Sensibilidad")
text(x = Sens_p, y = Sensib-0.05, label = round(Sensib,4), pos = 1, cex = 0.8, col = 
       "black")

Espe_p <- barplot(Espec, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="Especificidad")
text(x = Espe_p, y = Espec-0.05, label = round(Espec,4), pos = 1, cex = 0.8, col = 
       "black")

PPV_p <- barplot(PPV, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="Valor Predictivo Positivo")
text(x = PPV_p, y = PPV-0.05, label = round(PPV,4), pos = 1, cex = 0.8, col = "black")

NPV_p <- barplot(Kappa, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="Valor Predictivo Negativo")
text(x = NPV_p, y = NPV-0.05, label = round(NPV,4), pos = 1, cex = 0.8, col = "black")

F1_p <- barplot(F1, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="F1")
text(x = F1_p, y = F1-0.05, label = round(F1,4), pos = 1, cex = 0.8, col = "black")

AUC_p <- barplot(AUC, names.arg=c("kNN", "SVM", "RF", "ANN"), col = color,
        ylab=c("Proporcion"), main="AUC")
text(x = AUC_p, y = AUC, label = round(AUC,4), pos = 1, cex = 0.8, col = "black")

```

```{r}
print(sessionInfo())
```

# Congreso
```{r}
str(bc_s)
head(bc_s, 10)
``` 

```{R fig.width=9, fig.height=9}
par(mar=c(10,3,1,1))

means_n_s <- as.numeric((lapply(bc_s_n, mean)))

boxplot(bc_s_n[,-1], las=2, col="lightblue")
# , main="Figura 2. Distribucion de las variables del dataset normalizadas"
abline(h=mean(means_n_s), col="red")
``` 

```{r, fig.height=15, fig.width=15}
library(corrplot)
par(mar=c(11,3,1,1))

C <- cor(round(as.matrix(bc_n[1:30]), 4))

corrplot(C, method = "pie")

C2 <- cor(round(as.matrix(bc_s_n[1:9]),4))

corrplot(C2, method = "pie")
```

```{r}
(cm_knn_s)
(cm_svm_s)
(cm_rf_s)
```

```{r}
print("KNN")
cm_knn_s$overall[1]
cm_knn_s$overall[2]
cm_knn_s$byClass

print("SVM")
cm_svm_s$overall[1]
cm_svm_s$overall[2]
cm_svm_s$byClass

print("RF")
cm_rf_s$overall[1]
cm_rf_s$overall[2]
cm_rf_s$byClass
``` 

```{r fig.height=6, fig.width=18}
library(pROC)

# "royalblue","dodgerblue", "deepskyblue", "lightskyblue"

par(mfrow=c(1,3), pty="m")

plot.roc(model_knn_s$pred$obs,
         model_knn_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE, 
         col="royalblue", main = "Curva ROC para kNN")

plot.roc(model_svm_s$pred$obs,
         model_svm_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="dodgerblue", main = "Curva ROC para SVM")

plot.roc(model_rf_s$pred$obs,
         model_rf_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="deepskyblue", main = "Curva ROC para RF")

``` 

```{r fig.height=16, fig.width=12}

par(mfrow=c(4,3), pty="m")

#Acc <- c(max(knn_fit_n$results$Accuracy), 
#         max(model$results$Accuracy), 
#         max(rf_caret_model$results$Accuracy))

#Kappa <- c(max(knn_fit_n$results$Kappa),
#           max(model$results$Kappa), 
#           max(rf_caret_model$results$Kappa))

color <- c("royalblue", "dodgerblue", "deepskyblue")

Acc <- c(cm_knn_s$overall[1], cm_svm_s$overall[1], cm_rf_s$overall[1])
  
Kappa <- c(cm_knn_s$overall[2], cm_svm_s$overall[2], cm_rf_s$overall[2])

Sensib <- c(cm_knn_s$byClass[1], cm_svm_s$byClass[1], cm_rf_s$byClass[1])

Espec <- c(cm_knn_s$byClass[2], cm_svm_s$byClass[2], cm_rf_s$byClass[2])

PPV <- c(cm_knn_s$byClass[3], cm_svm_s$byClass[3], cm_rf_s$byClass[3])

NPV <- c(cm_knn_s$byClass[4], cm_svm_s$byClass[4], cm_rf_s$byClass[4])

F1 <- c(cm_knn_s$byClass[7], cm_svm_s$byClass[7], cm_rf_s$byClass[7])
  
AUC <- c(0.989, 0.996, 0.992)

times_3 <- times[1:3]

time_p <- barplot(as.vector(times_3), names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="Time")
text(x = time_p, y = times, label = round(times,3), pos = 1, cex = 0.8, col = "black")

Acc_p <- barplot(Acc, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="Exactitud (Accuracy)")
text(x = Acc_p, y = Acc-0.05, label = round(Acc,4), pos = 1, cex = 0.8, col = "black")

K_p <- barplot(Kappa, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="Kappa")
text(x = K_p, y = Kappa-0.05, label = round(Kappa,4), pos = 1, cex = 0.8, col = "black")

Sens_p <- barplot(Sensib, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="Sensititivy")
text(x = Sens_p, y = Sensib-0.05, label = round(Sensib,4), pos = 1, cex = 0.8, col = "black")

Espe_p <- barplot(Espec, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="Specificity")
text(x = Espe_p, y = Espec-0.05, label = round(Espec,4), pos = 1, cex = 0.8, col = "black")

PPV_p <- barplot(PPV, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="Positive Predictive Value")
text(x = PPV_p, y = PPV-0.05, label = round(PPV,4), pos = 1, cex = 0.8, col = "black")

NPV_p <- barplot(Kappa, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="Negative Predictive Value")
text(x = NPV_p, y = NPV-0.05, label = round(NPV,4), pos = 1, cex = 0.8, col = "black")

F1_p <- barplot(F1, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="F1")
text(x = F1_p, y = F1-0.05, label = round(F1,4), pos = 1, cex = 0.8, col = "black")

AUC_p <- barplot(AUC, names.arg=c("kNN", "SVM", "RF"), col = color,
        ylab=c("Proportion"), main="AUC")
text(x = AUC_p, y = AUC, label = round(AUC,4), pos = 1, cex = 0.8, col = "black")

plot.roc(model_knn_s$pred$obs,
         model_knn_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE, 
         col="royalblue", main = "ROC Curve for kNN")

plot.roc(model_svm_s$pred$obs,
         model_svm_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="dodgerblue", main = "ROC Curve for SVM")

plot.roc(model_rf_s$pred$obs,
         model_rf_s$pred$Malignant,
         smoothed = TRUE,
         legacy.axes=TRUE,
         # arguments for ci
         ci=TRUE, ci.alpha=0.9, stratified=FALSE,
         # arguments for plot
         #plot=TRUE, 
         auc.polygon=TRUE, 
         max.auc.polygon=TRUE, grid=TRUE,
         print.auc=TRUE, show.thres=TRUE,
         col="deepskyblue", main = "ROC Curve for RF")
``` 





